\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-15 manuscript/main.tex
scalar part has subscript K+1

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
	Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
	\end{equation*}
	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
Since functional predictors are observed at finitely many discrete time points in practice,
we use finite-dimensional projections obtained by the expansion truncating at $M$ terms.
We choose a moderately large value of $M$ (e.g., 15 or 20) to capture rich functional variation without requiring fine-tuning, as our method promotes smoothness through penalization (see Section~\ref{sec: Regularization of PLS Components}). We denote the truncated space by
	\begin{equation}
		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
	\end{equation}
	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notation for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}
The observations in the hybrid PLS problem can be compactly represented by the tuple
\begin{equation}\label{def:problem_instance}
	(\mathbb{B}, \Theta, \mathbf{y})
	\in
	,
\end{equation}
defined as follows.
First, let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
\begin{equation}
	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
	\quad
	B^{\prime\prime}_{m, m'} := \int_0^1 b^{\prime\prime}_m(t)\, b^{\prime\prime}_{m'}(t)\, dt,
\end{equation}
for $m, m' = 1, \ldots, M$.
Leveraging these notations, 
we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
\[
\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
\quad \text{and} \quad
\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
\]
We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
\in
\mathbb{R}^{n \times (MK+p)}
$ , and let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.

@@

	We now describe the strategy for computing the PLS component direction at the $l$-th iteration. For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
	The goal is to find a unit-norm direction $\xi \in 
	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
	 defined as
\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}}^2 \left( \langle 
	 	\widetilde{W},
	 	\xi \rangle_{\mathcal{H}}, Y \right)
	 	:=
	 	\biggl(
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	\biggr)^2
	 	.
	 \end{equation}
	We denote the maximizer as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
:= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
\| \xi  \|_\mathcal{H} = 1
 } \widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
\bigr)
	\end{equation}
%
	where each functional part $\hat{\xi}_j $  is expressed as
	\begin{equation*}
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
	\end{equation*}

@@

	\begin{proposition}\label{proposition:eigen_noregul}
Let
$
(\mathbb{B}, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, let
$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top )^\top$
denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
These coefficients are obtained by solving the following generalized eigenvalue problem:
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
\end{equation}

@@

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative $\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt$.
Instead of solely maximizing the squared empirical covariance
 $\widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_\mathcal{H}, Y 
\bigr)
$, 
we incorporate this roughness penalty to simultaneously control the complexity of the estimated functional components.

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense. As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}. This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness. Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.

@@

		\begin{equation*}
			\sum \limits_{k=1}^K \lambda_k \textnormal{PEN} \left(\psi^{(k)} \right) = \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
		\end{equation*}
		where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
		\begin{equation}\label{def:Lambda}
			\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
		\end{equation}
		$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

>>>>

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
	Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
	\end{equation*}
	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
Since functional predictors are observed at finitely many discrete time points in practice,
we use finite-dimensional projections obtained by the expansion truncating at $M$ terms.
We choose a moderately large value of $M$ (e.g., 15 or 20) to capture rich functional variation without requiring fine-tuning, as our method promotes smoothness through penalization (see Section~\ref{sec: Regularization of PLS Components}). We denote the truncated space by
	\begin{equation}
		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
	\end{equation}
	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notation for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}
The observations in the hybrid PLS problem can be compactly represented by the tuple
\begin{equation}\label{def:problem_instance}
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	\in
	\mathbb{R}^{(MK+p) \times (MK+p)}
	\times 
	\mathbb{R}^{(MK+p) \times (MK+p)}
	\times
	\mathbb{R}^{n \times (MK+p)}
	\times
	\mathbb{R}^{n}
	,
\end{equation}
defined as follows.
First, let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
\begin{equation}
	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
	\quad
	B^{\prime\prime}_{m, m'} := \int_0^1 b^{\prime\prime}_m(t)\, b^{\prime\prime}_{m'}(t)\, dt,
\end{equation}
for $m, m' = 1, \ldots, M$.
Leveraging these notations, 
we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
\[
\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
\quad \text{and} \quad
\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
\]
We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
\in
\mathbb{R}^{n \times (MK+p)}
$ , and let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.

@@

	We now describe the strategy for computing the PLS component direction at the $l$-th iteration. For simplicity, we omit the iteration index and assume that the observations have been residualized and are orthogonal to those from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for the residualization procedure).
	The goal is to find a unit-norm direction $\xi \in 
	(\mathcal{B}^K \times \mathbb{R}^p) \subset \mathcal{H}$ that maximizes the squared empirical covariance between the resulting PLS component scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$,
	 defined as
\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}}^2 \left( \langle 
	 	\widetilde{W},
	 	\xi \rangle_{\mathcal{H}}, Y \right)
	 	:=
	 	\biggl(
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	\biggr)^2
	 	.
	 \end{equation}
	We denote the maximizer as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
:= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
\| \xi  \|_\mathcal{H} = 1
 } \widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
\bigr)
	\end{equation}
%
	where each functional part $\hat{\xi}_j $  is expressed as
	\begin{equation*}
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{d}_{jm} \, b_m(t), \quad j = 1, \ldots, K.
	\end{equation*}

@@

\begin{proposition}\label{proposition:eigen_noregul}
Let
$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, let
$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
These coefficients are obtained by solving the following generalized eigenvalue problem:
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
\end{equation}

@@

	\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative $\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt$.
Instead of solely maximizing the squared empirical covariance
 $\widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_\mathcal{H}, Y 
\bigr)
$, 
we incorporate this roughness penalty to simultaneously control the complexity of the estimated functional components.

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
		\begin{align*}
	\sum \limits_{k=1}^K 
	\lambda_k 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
&=
	\sum \limits_{k=1}^K 
\lambda_k 
\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
\\&	 =
%%%%%%%%%%%%%%%%%%%
	\sum \limits_{k=1}^K 
\lambda_k 
\sum_{l=1}^M
\sum_{m=1}^M
\theta_{ijl} \theta_{ijm}
\int_0^1
 \, b_l^{\prime \prime}(t) 
  b_m^{\prime \prime}(t)
  dt
\\&	 =
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
\end{align*}
However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense. As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}. This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness. Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.

\begin{proposition}\label{proposition:eigen_noregul}
	Let
	$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	$
	denote the observed data defined in \eqref{def:problem_instance}.
	At the $l$-th iteration of the PLS algorithm, let
	$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
	These coefficients are obtained by solving the following generalized eigenvalue problem:
	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
		\left(
		\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
		\right)^\top
		=
		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
	\end{equation}
	where
	\begin{equation}\label{def:V_matrix}
		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
	\end{equation}

\end{proposition}

@@

		where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
		\begin{equation}\label{def:Lambda}
			\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
		\end{equation}
		$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.
